---
title: "resource selection coding"
output: github_document
---

```{r setup, include=FALSE}
#set working directory
setwd("C:/Users/marne/OneDrive/Documents/Thesis  Data/telemetry_data/elephant_spatial_data")
```
knitr::opts_chunk$set(echo = TRUE)
```{r load packages}
library(sp)
library(sf)
library(proxy)
library(raster)
library(adehabitatHR) 
library(amt)
library(dplyr)
library(lubridate)
library(forcats) # for collapsing landcover categories
library(ggmap)
library(ggplot2)
library(MuMIn)
library(sjPlot)
library(RWmisc)
library(tibble)
library(tidyr)
library(purrr)
library(broom)
```
```{r load data}
elemove <- read.csv('2020collars_tracker_data.csv',header=T, sep=",")
head(elemove)
str(elemove)
names(elemove)
```
```{r formatting data columns}
elemove$date_time_gmt <- as.POSIXct(elemove$Time.Stamp, tz = 'GMT', format = '%Y-%m-%d %H:%M:%S') ### this is in GMT, not Malawi time
elemove$date_time_lmt <- elemove$date_time_gmt # lmt = local mean time
attr(elemove$date_time_lmt, "tzone") <- 'Africa/Blantyre' # Africa/Blantyre time zone is Central Africa Time or GMT+02

# remove missed GPS fixes
elemove <- elemove[!grepl("N", elemove$Latitude),]

# convert lat lon to UTM
elemove$Latitude <- gsub("``", '" ', elemove$Latitude)
elemove$Latitude <- gsub("`", "' ", elemove$Latitude)
elemove$Latitude <- trimws(elemove$Latitude, 'left')
elemove$Longitude <- gsub("``", '" ', elemove$Longitude)
elemove$Longitude <- gsub("`", "' ", elemove$Longitude)
elemove$Longitude <- trimws(elemove$Longitude, 'left')

decimal_degrees <- dms2dd(elemove$Longitude, elemove$Latitude)
elemove <- cbind(elemove,decimal_degrees)
#str(elemove)
elemove <- st_as_sf(x = elemove, coords = c('lon', 'lat'), crs = 4326) # crs = coordinate reference system
elemove <- st_transform(elemove, crs = 32736)

elemove$x <- st_coordinates(elemove)[,1]
elemove$y <- st_coordinates(elemove)[,2]
#View(elemove)


#To add removing of locations from study area```
```{}

```

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
